---
title: "A brief introduction into light extraction using Bayesian methods as implemented in RLumSTARR"
author: "Sebastian Kreutzer"
date: "version: `r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{A brief introduction into light extraction using Bayesian methods as implemented in RLumSTARR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center"
)
library(RLumSTARR)
```

# Introduction

All examples shown below use a dataset shipped with package

# Bayesian analysis

## Import example files

```{r}
files <- list.files(system.file("extdata", "", package="RLumSTARR"), full.names=TRUE)
```

## Prepare data for the modelling

```{r, fig.width = 8}
## create curve array 
dat <- create_RFCurveArray(files = files)
plot(dat)
```

## Run the modelling

```{r}
##run modelling for one ROI
output <- extract_TRUELight(
 data = dat,
 ROI = c(5),
 stepping = 80,
 verbose = FALSE,
 method_control = list(
   n.chain = 3,
   n.iter = 50000,
   variable.names = c("mu", "phi", "omega", "epsilon"),
   thin = 20))
```

## Bayesian diagnostics

Bayesian diagnostics is important to check whether the parameters have 
converged. `'RLumSTARR'` returns the `mcmc.list` returned by `'rjags'`. 
In combination with the package `'coda'` (which is loaded once `'RLumSTARR'` is loaded). 
This can be used to get the hands on the data.

### Numerical summary
```{r}
summary(output$jags_output)
```

### Diagnostic plots

```{r, fig.width = 6, fig.height = 10}
plot(output$jags_output)
```
